quicR: An R Package for Real-Time Quaking Induced Conversion (RT-QuIC) Assays

### 2025-01-03 man/manuscript/manuscript.qmd
Update manuscript.

---
title: "quicR: An R Package for Real-Time Quaking Induced Conversion (RT-QuIC) Assays"
author:
    - name: 
        given: Gage
        family: Rowden
      id: GR
      orcid: 0000-0002-7517-0480
      email: rowde002@umn.edu
      affiliation:
        name: University of Minnesota
        city: Saint Paul
        state: MN
      roles:
        Conceptualization
        Methodology
        Software
        Validation
        Formal analysis
        Investigation
        Resources
        Data curation
        Writing--original draft preparation
        Writing--review and editing
        Visualization
        Supervision
        Prject administration
      corresponding: true
abstract: Real-time quaking induced conversion (RT-QuIC) has quickly become an emerging diagnostic tool for protein misfolding disorders such as Creutzfeldt-Jakob disease and Parkinson's disease. Given that the technology is still relatively new, academic and industry standards have yet to be established. 'quicR' was developed to fill this lack of standardization by providing functions for both data curation and analysis.
keywords: quicR, R package, RT-QuIC, prion, CJD, Parkinson's
format: pdf
mainfont: Calibri
bibliography: references.bib
bibliographystyle: apa
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(quicR)
library(dplyr)
library(kableExtra)
library(readxl)
library(readr)

@@

data.frame("Sample IDs" = samples) %>%
  mutate(
    Dilutions = -log10(dilutions),
    # Maxpoint Ratio
    MPR = calculate_MPR(df_norm, start_col = 3, data_is_norm = TRUE),
    # Max Slope
    MS = calculate_MS(df_norm, data_is_norm = TRUE),
    # Time to Threshold
    TtT = calculate_TtT(df_norm, threshold = 2, start_col = 3),
    # Rate of Amyloid Formation
    RAF = ifelse(TtT == hours, 0, 1 / TtT),
    # Crossed threshold?
    crossed = TtT != hours
  ) %>%
  head(15) %>%
  kable(row.names = FALSE)
```

@@

>>>>

---
title: "quicR: An R Package for Real-Time Quaking Induced Conversion (RT-QuIC) Assays"
author:
    - name: 
      given: Gage
      family: Rowden
      id: GR
      orcid: 0000-0002-7517-0480
      email: rowde002@umn.edu
      affiliation:
        name: University of Minnesota
        city: Saint Paul
        state: MN
      roles:
        Conceptualization
        Methodology
        Software
        Validation
        Formal analysis
        Investigation
        Resources
        Data curation
        Writing--original draft preparation
        Writing--review and editing
        Visualization
        Supervision
        Prject administration
      corresponding: true
    - name:
        given: Peter
        family: Larsen
        id: PL
        orcid: 0000-0000-0000-0000
        email: plarsen@umn.edu
        affiliation:
          name: University of Minnesota
          city: Saint Paul
          state: MN
        roles:
          Supervision
          Project administration
          Funding

abstract: Real-time quaking induced conversion (RT-QuIC) has quickly become an emerging diagnostic tool for protein misfolding disorders such as Creutzfeldt-Jakob disease and Parkinson's disease. Given that the technology is still relatively new, academic and industry standards have yet to be established. 'quicR' was developed to fill this lack of standardization by providing functions for both data curation and analysis. 
keywords: quicR, R package, RT-QuIC, prion, CJD, Parkinson's
format: pdf
mainfont: Calibri
bibliography: references.bib
bibliographystyle: apa
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(quicR)
library(dplyr)
library(kableExtra)
library(readxl)
library(readr)
library(ggplot2)
library(reshape2)

@@

df_analyzed <- data.frame("Sample IDs" = samples, check.names = FALSE) %>%
  mutate(
    Dilutions = -log10(dilutions),
    # Maxpoint Ratio
    MPR = calculate_MPR(df_norm, start_col = 3, data_is_norm = TRUE),
    # Max Slope
    MS = calculate_MS(df_norm, data_is_norm = TRUE),
    # Time to Threshold
    TtT = calculate_TtT(df_norm, threshold = 2, start_col = 3),
    # Rate of Amyloid Formation
    RAF = ifelse(TtT == hours, 0, 1 / TtT)
  )

df_analyzed%>%
  head(15) %>%
  kable(row.names = FALSE)
```

@@

### Plate View
```{r, warning=FALSE}
#| fig-width: 8
#| fig-height: 7
sample_locations <- get_sample_locations(
  file, 
  dilution_bool = TRUE,
  dilution_fun = function(x) -log10(x)
)

plate_view(df_, sample_locations)
```

### Summary Plots
```{r, warning=FALSE, message=FALSE}
#| fig-width: 6
#| fig-height: 5
df_analyzed %>%
  melt(id.vars = c("Sample IDs", "Dilutions")) %>%
  mutate_at("Dilutions", as.factor) %>%

  ggplot(aes(`Sample IDs`, value, fill = Dilutions)) +
    geom_boxplot() +
    facet_wrap(~variable, scales = "free")
```
